### 2020-03-17 abs.tex
Update abs.tex
push

We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.

@@

Our analysis shows that understanding the temporal course of asymptomatic transmission after infection can be important for assessing the importance of this route of transmission, and for disease dynamics as a whole. This provides an additional motivation for investigating these time distributions.

>>>>

We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.

@@

Our analysis shows that understanding the temporal course of asymptomatic transmission after infection can be important for assessing the importance of this route of transmission, and for disease dynamics as a whole. This provides an additional motivation for investigating both the prevalence and relative duration of asymptomatic transmission.

### 2020-03-17 research.in.context.tex
push

We use a mathematical model to assess how the time scale of asymptomatic transmission affects the epidemic potential for COVID-like pathogens.
We compare the basic reproduction number and the proportion of secondary cases caused by asymptomatic individuals during the initial exponential growth period across a wide range of assumptions about asymptomatic transmission.
These assumptions broadly fall under two opposite scenarios: asymptomatic individuals can have fast clearance (and therefore, faster transmission) or slow viral replication (and therefore, persistent infection and slower transmission).
If asymptomatic transmission is slower than symptomatic transmission, the basic reproduction number can be underestimated if asymptomatic transmission is not explicitly taken into account.
If asymptomatic transmission is faster than symptomatic transmission, asymptomatic transmission may still account for a large fraction of secondary infection.

>>>>

We use a mathematical model to assess how the time scale of asymptomatic transmission affects the epidemic potential for COVID-like pathogens.
We compare the basic reproduction number and the proportion of secondary cases caused by asymptomatic individuals during the initial exponential growth period across a wide range of assumptions about asymptomatic transmission.
These assumptions broadly fall under two opposite scenarios: asymptomatic individuals can have fast clearance (and therefore, faster transmission) or persistent infection (and therefore, slower transmission).
If asymptomatic transmission is slower than symptomatic transmission, the basic reproduction number can be underestimated if asymptomatic transmission is not explicitly taken into account.
If asymptomatic transmission is faster than symptomatic transmission, asymptomatic transmission may still account for a large fraction of secondary infection.

### 2020-03-17 short.body.tex
need to take a break
ok done?
push

There is significant ongoing interest in asymptomatic infections in COVID-19 \citep{chan2020familial, pan2020asymptomatic, tangearly} and their transmission potential \citep{bai2020presumed} for two major reasons.
First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.

@@

We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals (i.e., the rate at which new infections occur in the population) as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \citep{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
individuals with subclinical infections may have fast clearance and short generation intervals, or slow viral reproduction and long generation intervals (cf. \citep{roberts2007model}).
The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.

>>>>

There is significant ongoing interest in asymptomatic infections in COVID-19 \citep{chan2020familial, pan2020asymptomatic, tangearly} and their transmission potential \citep{bai2020presumed} for two major reasons.
First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
Given that 86\% of the cases were undocumted in Wuhan prior to travel restriction and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play important role in the transmission of COVID-19.

@@

We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals (i.e., the rate at which new infections occur in the population) as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \citep{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
individuals with subclinical infections may have fast clearance and short generation intervals, or persistent infection and long generation intervals (cf. \citep{roberts2007model}).
The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
